---
title: "plotly-lines"
author: "Adham Rishmawi"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{plotly-lines}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(NeglectR)
```


## line graphs

Frequently employed to depict fluctuations over time, line graphs embody one of the most popular chart types within the data visualization suite of tools known as Plotly utilized in R. A dynamic library capable of producing charts with user interaction features, Planoly requires x-y input data points (where x denotes time), while y denotes numerical measurement values to produce its visualizations. 

For example here is an implementation case for generating straight forward linear graphs through Poltoly.

Before creating linegraphs, we need to load the plotly package into our working environment.

```{r load-plotly, message = FALSE, warning=FALSE}
library(plotly)
library(tidyr)
```

## loading data

```{r}
data <- read.csv('http://sldr.netlify.com/data/zshal.csv')

```

## graph examples
```{r}
plot_ly(data, x = ~TagDay, y = ~DepthAvg, type = "scatter", mode = "lines",
        color = ~TransClass, colors = c("blue", "red", "green", "purple"),
        hoverinfo = "text", text = ~paste("Tag ID: ", TagID, "<br>Tag Day: ", TagDay, "<br>Depth Avg: ", DepthAvg)) |>
# Add chart title and axis labels
  layout(title = "Depth Average by Tag Day and Transmission Class",
            xaxis = list(title = "Tag Day"),
            yaxis = list(title = "Depth Average (meters)"))
```

this graph is horrible so lets make a better one!

```{r}
plot_ly(data, x = ~DepthAvg, y = ~TagID, type = "scatter",
        color = ~TransClass, colors = c("blue", "red", "green", "purple"),
        hoverinfo = "text", text = ~paste("Tag ID: ", TagID, "<br>Tag Day: ", TagDay, "<br>Depth Avg: ", DepthAvg))|>

# Add chart title and axis labels
  layout(title = "Depth Average by Tag Day and Transmission Class",
            xaxis = list(title = "Depth Average (meters)"),
            yaxis = list(title = "Tag day"))
```

much better because it isnt a line graph!!

